\subsection{Sensitivity Analysis}
	A literature review was conducted to assess which and how SWAT parameters have been adjusted in other projects. We carried out a one-at-a-time sensitivity analysis for the parameters found in the literature as well as others thought to be of interest in calibrating the model. By one-at-a-time sensitivity analysis we mean that the model was run a set number of times, in this case, for twenty-five iterations and for each of these iterations only one parameter was adjusted, and the model output collected. In this way the effect of one parameter could be isolated and its impact on the model assessed. 

	For each parameter minimum and maximum values were set, from which parameter ranges were created; the parameter ranges defined the increments upon which the iterations were run. The minimum and maximum parameter values were determined based upon the literature review and what parameter values were deemed realistic. For example, parameters affecting snowmelt can be set to melt snow at -20\degree C  to 20\degree C, but it was thought more realistic to set the minimum and maximum parameter values to 0.5\degree C  and 2.5\degree C. Some parameters were adjusted absolutely and others were adjusted relatively, depending on how much was known about their response or if the parameters varied geographically. The parameter ALPHA\_BF, which adjusts the amount of baseflow to a reach was regionalized based on regression analysis and so varied throughout the basin; thus ALPHA\_BF ranges were defined based on a percentage (i.e., plus and minus five percent of the initial value). The parameters included in the sensitivity analysis are shown in Table \ref{tab:sens_anl}. 

	During the sensitivity analysis, after each model run the model output was collected. The output that was collected varied based on which parameter was being run. For groundwater, soil, management, hru and basin parameters water yield was collected, found in the output.sub output file. This output reports the amount of water generated by the land area in the subwatershed. Reach parameters do not have an affect upon the amount of water leaving the landscape and so streamflow information from the output.rch file was used to assess how changes in these parameters affect the model.
	
	Sensitivity was assessed by calculating the change in model output for each subbasin from one iteration to the next. This was accomplished by subtracting the subsequent iteration from each iteration and then taking the mean of the absolute values of these differences. This value then represents the mean annual change in model output expected from a change in target parameter value. 

	% This sensitivity analysis was coded in R and setup to run on multiple processors at once.

\pagebreak